---
title: "Markdown Report"
author: "Suada Pastacaldi"
date: "2024-01-09"
output: html_document

---

# My first markdown document
to open markdown document, 
new file, .Rmd

eval is "evaluation" if we want the text to be avaluated or not
if it is-> code is in grey boxes and undernith we have the results in withe box

```{r, eval=T}
2+3
```
 
if not result 
```{r, eval=F}
2+3
```

Using proper packages:
library for remote sensing
```{r, eval=T}
library(imageRy)
```

Import data 
```{r, eval=T}
im.list()
```
```{r, eval=T, warning=FALSE}
mato<-im.import("matogrosso_ast_2006209_lrg.jpg")
```

```{r, eval=T}
mato 
```

im.plotRGB
new plot with nir on top of green 
```{r, eval=T}
im.plotRGB(mato, 2,1,3)
```

Avvertimento: [rast] unknown extent
use echoing=F
or in this case warning=F


plot images toghether
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(mato, 2,1,3)
im.plotRGB(mato, 1,2,3)
im.plotRGB(mato, 2,3,1)
im.plotRGB(mato, 3,1,2)
```


compute spectral indeces
```{r, eval=T, warning=F}
library(viridis)
library(terra)
viridisc <- colorRampPalette(viridis(7))(255)
#dvi<-mato[1]-mato[2]

```
